paper

### 2024-09-27 inst/extdata/paperdata/paper.qmd

@@

soma0.5 <- soma[, sample(1:262, 262) , drop = FALSE]

set.seed(1234, kind = "default")
keep_samples <- colData(soma0.5)$CNO != 12
soma0.5 <- soma0.5[, keep_samples]

@@

limrots.result2 <- LimROTS(data.exp = soma0.5, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, progress = TRUE, seed.cl = 1234)

@@

>>>>

```{r}
{r}
# Load necessary packages
library(LimROTS)
library(parallel)
library(SummarizedExperiment)
# Load the dataset
data("proteogenomicPD")
print(soma)

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma@colData@listData)
B <- 1000  # Number of bootstrap samples
K <- dim(soma)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

limrots.result <- LimROTS(data.exp = soma, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, progress = TRUE, seed.cl = 1234)

```{r}
plot(limrots.result2$q_values)
hist(limrots.result2$q_values)
hist(limrots.result2$q_values$qvalues)
hist(limrots.result2$FDR)

@@

soma0.5 <- soma[, sample(1:524, 393) , drop = FALSE]

keep_samples <- colData(soma0.5)$CNO %in% names(which(table(colData(soma0.5)$CNO) <= 2))
soma0.5 <- soma0.5[, !keep_samples]

@@

soma0.5 <- LimROTS(data.exp = soma0.5, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, progress = TRUE, seed.cl = 1234)

@@

```{r}
plot(soma0.5$q_values)
hist(soma0.5$q_values)
hist(soma0.5$q_values$qvalues)
hist(soma0.5$FDR)

summary(soma0.5$q_values)
```
